Figure 6 - networks

### 2024-07-05 ms_figure_6_networks.Rmd
Rearrange Fig 6, add new panels

---
title: "Figure 5 - networks"
author: "Charlotte Soneson, Michael Stadler, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    rds150: "data/ipms_150_sce.rds"
    coords150: "data/visnetwork_coords_150_new.csv"
    rds500: "data/ipms_500_sce.rds"
    coords500: "data/visnetwork_coords_500_new.csv"
    rds150untag: "data/ipms_150_untag_sce.rds"
    interactors: "data/Gene_list_TFinteractors_Pombase20240226.txt"
    idmap: "data/id_mapping_table.txt"
    rad24_rad25_tbl: "data/FigS5_Rad24_Rad25_interactingTFs_list_motifs.txt"
editor_options: 
    chunk_output_type: console
---

@@

```{r load-packages, class.source="fold-show"}
suppressPackageStartupMessages({
    library(visNetwork)
    library(SingleCellExperiment)
    library(dplyr)
    library(ggplot2)
    library(igraph)
    library(shiny)
    library(cowplot)
    library(ggplotify)
    library(ggraph)
    library(latex2exp)
    library(tidygraph)
    library(ggrepel)
    library(ComplexHeatmap)
    library(flextable)
    library(kableExtra)
    library(tidyr)
})

@@

# Figure 5

@@

```{r Fig5}
#| fig.width: 10
#| fig.height: 10

@@

cowplot::plot_grid(
    fig5a, 
    cowplot::plot_grid(
        cowplot::plot_grid(
            ggr150 + theme(legend.position = "none"), 
            ggr500 + theme(legend.position = "none"), 
            nrow = 1, labels = c("B", "C")
        ),
        get_legend(ggr150 + theme(legend.position = "bottom"), "bottom"),
        nrow = 2, labels = c("", ""), rel_heights = c(1, 0.25)
    ), ncol = 1, rel_heights = c(1, 2)
)
```

@@

```{r suppFig5}
#| fig.width: 9
#| fig.height: 10

## Get all t-statistics and visualize
res150untag <- .getTestCols(sce150untag, adjp_cutoff = 0.01, logfc_cutoff = 1)
rad <- res150untag$tstat[c("Rad24", "Rad25"), ]
colnames(rad) <- .getProteinNameFromComparison(colnames(rad))
rad <- t(rad)
hmrad <- Heatmap(rad, 
                 cluster_rows = TRUE, 
                 cluster_columns = FALSE, 
                 col = circlize::colorRamp2(
                     breaks = seq(1.5, 13.0, length.out = 64),
                     colors = colorRampPalette(
                         binary_heatmap_colors[c("FALSE", "TRUE")])(64)),
                 border = TRUE, 
                 border_gp = gpar(lwd = 0.5),
                 name = "Mod.\nt-stat.",
                 na_col = binary_heatmap_colors["FALSE"],
                 column_names_gp = gpar(fontsize = fl),
                 row_names_gp = gpar(fontsize = fs),
                 show_row_names = TRUE, 
                 show_column_names = TRUE, 
                 use_raster = FALSE,
                 show_heatmap_legend = TRUE, 
                 width = unit(w_trad / 1.5, "mm"), 
                 heatmap_height = unit(1.3 * h_trad, "mm"),
                 column_title_gp = gpar(fontsize = ft),
                 heatmap_legend_param = list(
                     title_gp = gpar(fontsize = fl),
                     border = "gray10",
                     border_gp = gpar(lwd = 0.5)
                 ))
set.seed(42L)
hm_rad <- grid.grabExpr(
    hmrad <- draw(hmrad, merge_legend = TRUE,
                 heatmap_legend_side = "right",
                 annotation_legend_side = "right"),
    width = w_trad / 1.5, height = 1.3 * h_trad
)

## List of experiments where rad24 and/or rad25 were pulled down
comps <- colnames(res150untag$interactor)[colSums(
    res150untag$interactor[c("Rad24", "Rad25"), ], na.rm = TRUE) > 0]
explist <- .getUniProtIdFromComparison(comps,idmap = idmap)
cat(explist)
gnames <- .getProteinNameFromComparison(comps)
cat(gnames)

plot_grid(hm_rad, ggtbl, nrow = 1, align = "h", axis = "b", 
          rel_widths = c(2, 2.5), labels = c("A", "B"))
```

>>>>

---
title: "Figure 6 - networks"
author: "Charlotte Soneson, Michael Stadler, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    rds150: "data/ipms_150_sce.rds"
    coords150: "data/visnetwork_coords_150_new.csv"
    rds500: "data/ipms_500_sce.rds"
    coords500: "data/visnetwork_coords_500_new.csv"
    rds150untag: "data/ipms_150_untag_sce.rds"
    interactors: "data/Gene_list_TFinteractors_Pombase20240226.txt"
    idmap: "data/id_mapping_table.txt"
    rad24_rad25_tbl: "data/FigS5_Rad24_Rad25_interactingTFs_list_motifs.txt"
editor_options: 
    chunk_output_type: console
---

@@

```{r load-packages, class.source="fold-show"}
suppressPackageStartupMessages({
    library(visNetwork)
    library(SingleCellExperiment)
    library(dplyr)
    library(ggplot2)
    library(igraph)
    library(shiny)
    library(cowplot)
    library(ggplotify)
    library(ggraph)
    library(latex2exp)
    library(tidygraph)
    library(ggrepel)
    library(ComplexHeatmap)
    library(flextable)
    library(kableExtra)
    library(ggupset)
    library(tidyr)
})

@@

# 14-3-3 protein interactions

```{r rad24-rad25}
#| fig.width: 9
#| fig.height: 15

## Get all t-statistics and visualize
res150untag <- .getTestCols(sce150untag, adjp_cutoff = 0.01, logfc_cutoff = 1)
rad <- res150untag$tstat[c("Rad24", "Rad25"), ]
colnames(rad) <- .getProteinNameFromComparison(colnames(rad))
rad <- t(rad)
hmrad <- Heatmap(rad, 
                 cluster_rows = TRUE, 
                 cluster_columns = FALSE, 
                 col = circlize::colorRamp2(
                     breaks = seq(1.5, 13.0, length.out = 64),
                     colors = colorRampPalette(
                         binary_heatmap_colors[c("FALSE", "TRUE")])(64)),
                 border = TRUE, 
                 border_gp = gpar(lwd = 0.5),
                 name = "Mod.\nt-stat.",
                 na_col = binary_heatmap_colors["FALSE"],
                 column_names_gp = gpar(fontsize = fl),
                 row_names_gp = gpar(fontsize = fs),
                 show_row_names = TRUE, 
                 show_column_names = TRUE, 
                 use_raster = FALSE,
                 show_heatmap_legend = TRUE, 
                 width = unit(w_trad / 1.5, "mm"), 
                 heatmap_height = unit(1.4 * h_trad, "mm"),
                 column_title_gp = gpar(fontsize = ft),
                 heatmap_legend_param = list(
                     title_gp = gpar(fontsize = fl),
                     border = "gray10",
                     border_gp = gpar(lwd = 0.5)
                 ))
set.seed(42L)
hm_rad <- grid.grabExpr(
    hmrad <- draw(hmrad, merge_legend = TRUE,
                 heatmap_legend_side = "right",
                 annotation_legend_side = "right"),
    width = w_trad / 1.5, height = 1.4 * h_trad
)

## List of experiments where rad24 and/or rad25 were pulled down
comps <- colnames(res150untag$interactor)[colSums(
    res150untag$interactor[c("Rad24", "Rad25"), ], na.rm = TRUE) > 0]
explist <- .getUniProtIdFromComparison(comps, idmap = idmap)
cat(explist)
gnames <- .getProteinNameFromComparison(comps)
cat(gnames)

# UpSet plot
dfupset <- as.data.frame(t(res150untag$interactor[c("Rad24", "Rad25"), ])) |>
    tibble::rownames_to_column("TF") |>
    dplyr::mutate(TF = .getProteinNameFromComparison(TF))

ovL <- as.list(as.data.frame(dfupset[, c("Rad24", "Rad25")]))
ovL <- lapply(ovL, function(i) dfupset$TF[which(i)])

pd <- stack(ovL) |>
    group_by(values) |>
    summarise(ind = list(ind)) |>
    dplyr::left_join(rad24_rad25_tbl, by = join_by("values" == "TF")) |>
    dplyr::mutate(has_motif = !is.na(`R-x-x-[S/T]-x-P`) & `R-x-x-[S/T]-x-P` != "")

ggrad_upset <- ggplot(pd, aes(x = ind)) +
    geom_bar(aes(fill = has_motif)) +
    scale_fill_manual(values = c(`TRUE` = main_colors[3], `FALSE` = main_colors[5])) +
    scale_x_upset() +
    labs(x = element_blank(), y = "Number of IPs", fill = "Has motif: ") +
    theme_cowplot(12) +
    theme(axis.ticks.x = element_blank(),
          legend.position = "bottom") +
    theme_combmatrix(combmatrix.label.extra_spacing = 5,
                     combmatrix.label.make_space = TRUE,
                     combmatrix.label.width = unit(18, "mm")) +
    guides(fill = guide_legend(nrow = 1))
```

# Figure 6

@@

```{r Fig6}
#| fig.width: 10
#| fig.height: 10

fig6c <- ggdraw() + 
    draw_image("schematics/Fig6C_Pho7_protein_domains_cartoon_Arial_RGB.png")

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        cowplot::plot_grid(
            ggr150 + theme(legend.position = "none"), 
            ggr500 + theme(legend.position = "none"), 
            nrow = 1, labels = c("A", "B")
        ),
        get_legend(ggr150 + theme(legend.position = "bottom"), "bottom"),
        nrow = 2, labels = c("", ""), rel_heights = c(1, 0.25)
    ),
    cowplot::plot_grid(fig6c, ggrad_upset,
                       nrow = 1, labels = c("C", "D")), 
    rel_heights = c(5, 2), 
    ncol = 1
)
```

@@

```{r suppFig6}
#| fig.width: 9
#| fig.height: 15

plot_grid(
    fig5a, 
    plot_grid(hm_rad, ggtbl, nrow = 1, align = "h", axis = "b", 
              rel_widths = c(2, 2.5), labels = c("B", "C")),
    rel_heights = c(1, 3), ncol = 1,
    labels = c("A", "")
)
```
